Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-05-25 cvx-flats-neurips21/cvx-flats.tex
comment on flats

\begin{restatable}{theorem}{convexflats}  \label{thm:convex-flats-inf-dim}
  Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by $L \in \Lcvx_d$ for some $d\in\mathbb{N}$.
  Let $\Y$ be either a finite set, or $\Y = \reals$, in which case we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.%
  \footnote{This assumption is largely for technical convenience, to ensure that $\V_{u,p}$ does not depend on $p$.
    Any such assumption would suffice, and we suspect even that condition can be relaxed.}
  For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
\end{restatable}
\begin{proof}[Finite case]
  We will prove the result for the case of finite $\Y$, and defer the $Y=\reals$ case to Appendix~\ref{app:implications-of-bounds}.
  As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
  With $\Y$ finite, this is additionally equivalent to $\vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.\footnote{$\partial$ represents the subdifferential $\partial f(x) = \{z : f(x') - f(x) \geq \inprod{z}{x'-x}\; \forall x' \}$.}
  Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y \mid x_y \in \partial L(u,y) \; \forall y\in\Y\}$, and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$; cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
  Let $V_{u,p} : \Y \to \reals^d, y \mapsto W_y$ be the function encoding the columns of $W$.
  Observe that $\E_p V_{u,p} = \vec 0$.				 
  We take the flat $F := \zeros{V_{u,p}}$, and have $p \in F$ by construction.
  To see $F \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\P$ that $q \in \zeros{V_{u,p}} \implies \vec 0 \in \partial \E_q L(u,Y) \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
\end{proof}

>>>>

\begin{restatable}{theorem}{convexflats}  \label{thm:convex-flats-inf-dim}
  Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by $L \in \Lcvx_d$ for some $d\in\mathbb{N}$.
  Let $\Y$ be either a finite set, or $\Y = \reals$, in which case we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.%
  \footnote{This assumption is largely for technical convenience, to ensure that $\V_{u,p}$ does not depend on $p$.
    Any such assumption would suffice, and we suspect even that condition can be relaxed.}
  For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
\raft{Suggestion: let's ditch $V_{u,p}$ in the statement, and instead say ``there is some $d$-flat $F$ such that $p \in F \subseteq \Gamma_u$'', since (a) that's the way we write it everywhere else, (b) we justify the story that our main tool is about $d$-flats, and (c) it becomes clearer why the two Corollaries could follow.  Am I missing a reason to keep $V_{u,p}$?}
\end{restatable}
\begin{proof}[Finite case]
  We will prove the result for the case of finite $\Y$, and defer the $Y=\reals$ case to Appendix~\ref{app:implications-of-bounds}.
  As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
  With $\Y$ finite, this is additionally equivalent to $\vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.\footnote{$\partial$ represents the subdifferential $\partial f(x) = \{z : f(x') - f(x) \geq \inprod{z}{x'-x}\; \forall x' \}$.}
  Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y \mid x_y \in \partial L(u,y) \; \forall y\in\Y\}$, and thus $W p = \sum_y p_y x_y = \vec 0$ where $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$; cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
  Let $V_{u,p} : \Y \to \reals^d, y \mapsto W_y$ be the function encoding the columns of $W$.
  Observe that $\E_p V_{u,p} = \vec 0$.				 
  We take the flat $F := \zeros{V_{u,p}}$, and have $p \in F$ by construction.
  To see $F \subseteq \Gamma_u$, from the chain of equivalences above, we have for any $q\in\P$ that $q \in \zeros{V_{u,p}} \implies \vec 0 \in \partial \E_q L(u,Y) \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
\end{proof}
